\begin{finalbox}{}
\titlee{American Pie}
\end{finalbox}{}

\begin{enumerate}
\myverse{ \acc{A} \acc{G} long \acc{D} long \acc{Em}7 time ago \\ 
\acc{Am} I can still re-\acc{C}-member \\ 
how that \acc{Em} music used to make me \acc{D} smile. \\ 
And \acc{G} I knew \acc{D} if I \acc{Em}7 had my chance \\ 
that \acc{Am} I could make those \acc{C} people dance and \\ 
\acc{Em} maybe they’d be \acc{C} happy for a \acc{D} while. \\ 
But \acc{Em} February \acc{Am} made me shiver \\ 
\acc{Em} with every paper \acc{Am} I’d deliver \\ 
\acc{C} Bad news \acc{G} on the \acc{Am} doorstep \\ 
I \acc{C} couldn’t take one \acc{D} more step \\ 
I \acc{G} can’t re-\acc{D}-member if I \acc{Em} cried when I \\ 
\acc{Am7} read about his \acc{D} widowed bride \\ 
But \acc{G} something \acc{D} touched me \acc{Em} deep inside \\ 
the \acc{C} day the \acc{D7} music \acc{G} died (\acc{C}-G) \acc{D} \\ 
 }

\myrefrain[]{Refrain:}{ \acc{G} Bye \acc{C} bye Miss \acc{A}-\acc{G}-merican \acc{D} Pie. \\ 
Drove my \acc{G} chevy to the \acc{C} levy \\ 
but the \acc{G} levy was \acc{D} dry \\ 
And them \acc{G} good old \acc{C} boys \\ 
were drinking \acc{G} whiskey and \acc{D} rye \\ 
Singin’ \acc{Em} this’ll be the day that I \acc{A7} die \\ 
\acc{Em} this’ll be the day that I \acc{D7} die. }

\myverse{ \acc{G} Did you write the \acc{Am} book of love and \\ 
do \acc{C} you have faith in \acc{Am} God above? \\ 
\acc{Em} If the Bible \acc{D} tells you so. \\ 
Do \acc{G} you be-\acc{D}-lieve in \acc{Em} Rock ’n Roll? \\ 
Can \acc{Am7} music save your \acc{C} mortal soul? \\ 
And \acc{Em} can you teach me \\ 
\acc{A7} how to dance \acc{D} real slow? \\ 
Well, I \acc{Em} know that you’re in \acc{D} love with him \\ 
’cause I \acc{Em} saw you dancin’ \acc{D} in the gym \\ 
You \acc{C} both kicked \acc{G} off your \acc{A7} shoes. \\ 
Man, I \acc{C} dig those rhythm’n \acc{D7} blues \\ 
I was a \acc{G} lonely \acc{D} teenage \acc{Em} broncin’ buck \\ 
with a \acc{Am} pink carnation and a \acc{C} pickup truck. \\ 
But \acc{G} I knew \acc{D} I was \acc{Em} out of luck the \acc{C} day \\ 
the \acc{D7} music \acc{G} died \acc{C} \\ 
\acc{G} I started \acc{D} singin’ \Reff }

\myverse{ \acc{G} Now for ten years we’ve been \acc{Am} on our own \\ 
and \acc{C} moss grows fat on a \acc{Am} rollin’ stone \\ 
\acc{Em} But that’s not how it \acc{D} used to be. \\ 
When the \acc{G} jester \acc{D} sang \\ 
for the \acc{Em} King and Queen \\ 
In a \acc{Am7} coat he borrowed \acc{C} from James Dean \\ 
and a \acc{Em} voice that came from \acc{A7} you and \acc{D} me \\ 
Oh, and \acc{Em} while the King was \acc{D} looking down \\ 
the \acc{Em} jester stole his \acc{D} thorny crown \\ 
The \acc{C} courtroom \acc{G} was ad-\acc{A7}-journed, \\ 
no Cverdict was re\acc{D}7turned \\ 
And while \acc{G} Lenin \acc{D} read a \acc{Em} book of Marx \\ 
the \acc{Am} court kept practice \acc{C} in the park \\ 
And \acc{G} we sang \acc{D} dirges \acc{Em} in the dark the \acc{C} day \\ 
the \acc{D7} music \acc{G} died. \acc{C} \\ 
\acc{G} We were \acc{D} singing \Reff }

\myverse{ \acc{G} Helter-Skelter in a \acc{Am} summer swelter \\ 
the \acc{C} Byrds flew off with a \acc{Am} fallout shelter \\ 
\acc{Em} Eight Miles High and \acc{D} falling fast, \\ 
it \acc{G} landed \acc{D} foul out \acc{Em} on the grass \\ 
The \acc{Am7} players tried \acc{C} for a forward pass but \\ 
the \acc{Em} jester’s on the \acc{A7} sidelines in a \acc{D} cast \\ 
Now the \acc{Em} half-time air was \acc{D} sweet perfume \\ 
while the \acc{Em} sergeants played \\ 
a \acc{D} marching tune \\ 
\acc{C} We all \acc{G} got up to \acc{A7} dance \\ 
but we \acc{C} never got \acc{D7} the chance \\ 
’cause the \acc{G} players \acc{D} tried to \acc{Em} take the field. \\ 
The \acc{Am} marching band re-\acc{C}-fused to yield \\ 
\acc{G} Do you \acc{D} recall \acc{Em} what was revealed \\ 
the \acc{C} day the \acc{D7} music \acc{G} died? \acc{C} \\ 
\acc{G} We started \acc{D} singing \Reff }

\myverse{ \acc{G} Oh, and there we were all \acc{Am} in one place, \\ 
a \acc{C} generation \acc{Am} Lost in Space \\ 
\acc{Em} With no time left to \acc{D} start again \\ 
So come on, \acc{G} Jack be nimble \acc{Em} Jack be quick \\ 
Jack \acc{Am7} Flash sat on a \acc{C} candlestick ’cause \\ 
\acc{Em} fire is the \acc{A7} Devil’s only \acc{D} friend \\ 
Oh, and \acc{Em} as I watched him \acc{D} on the stage \\ 
my \acc{Em} hands were clenched in \acc{D} fists of rage \\ 
\acc{C} No angel \acc{G} born in \acc{A7} hell, \\ 
could \acc{C} break that Satan’s \acc{D7} spell \\ 
And as the \acc{G} flames climbed \acc{D} high in-
\acc{Em}-to the night to \acc{Am} light the sacri-\acc{C}-fical rite \\ 
I saw \acc{G} Satan \acc{D} laughing \acc{Em} with delight, \\ 
the \acc{C} day the \acc{D7} music \acc{G} died \acc{C} \\ 
\acc{G} He was \acc{D} singing \Reff }

\myverse{ I \acc{G} met a \acc{D} girl who \acc{Em} sang the Blues \\ 
and I \acc{Am} asked her for some \acc{C} happy news \\ 
But \acc{Em} she just smiled and turned \acc{D} away \\ 
I \acc{G} went down \acc{D} to the \acc{Em} sacred store \\ 
Where \acc{Am7} I heard the music \\ 
\acc{C} years before \\ 
but the \acc{Em} man there \\ 
said the \acc{C} music wouldn’t \acc{D} play \\ 
And in the \acc{Em} streets \\ 
the \acc{Am} children screamed the \acc{Em} lovers cried, \\ 
and the \acc{Am} poets dreamed \\ 
But \acc{C} not a \acc{G} word was \acc{Am} spoken \\ 
the \acc{C} Church bells all were \acc{D} broken \\ 
And the \acc{G} three men \acc{D} I ad-\acc{Em}-mire most, \\ 
the \acc{C} Father, Son and the \acc{D7} Holy Ghost \\ 
They \acc{G} caught the \acc{D} last train \acc{Em} for the coast, \\ 
the \acc{C} day the \acc{D7} music \acc{G} died. \acc{C} \\ 
And \acc{G} they were \acc{D} singing \Reff }

\end{enumerate}