\title{Father and Son} 

%\begin{enumerate}
It’s not \acc{G} time to make a \acc{D} change, \\ 
just re\acc{C} lax, take it \acc{Am}7 easy, \\ 
you’re still \acc{G} young, that’s your \acc{Em} fault, \\ 
there’s so \acc{Am} much you have to \acc{D} know. \\ 
Find a \acc{G} girl, settle \acc{D} down, \\ 
if you \acc{C} want you can \acc{Am}7 marry, \\ 
look at \acc{G} me I am \acc{Em} old but I’m \acc{Am} happy. \acc{D} \\ 
I was \acc{G} once like you are \acc{D} now, \\ 
and I \acc{C} know that it’s not \acc{Am}7 easy \\ 
to be \acc{G} calm, when you’ve \acc{Em} found \\ 
something going \acc{Am} on. \acc{D} \\ 
But take your \acc{G} time, think a \acc{D} lot, \\ 
think of \acc{C} everything you’ve \acc{Am}7 got \\ 
for you will \acc{G} still be here \acc{Em} tomorrow, \\ 
but your \acc{D} dreams may not.\acc{G} \\ 
How can \acc{G} I try to ex\acc{D}plain, \\ 
when I \acc{C} do he turns a\acc{Am}7 way again, \\ 
it’s \acc{G} always been the \acc{Em} same, same old \acc{Am} \\ 
story. \acc{D}

From the \acc{G} moment I could \acc{D} talk, \\ 
I was \acc{C} ordered to \acc{Am}7 listen, \\ 
now there’s a \acc{G} way and I \acc{Em} know, that I \acc{D} have \\ 
to \acc{G} go away. \\ 
I \acc{D} know, I \acc{C} have to \acc{G} go. \\ 
It’s not \acc{G} time to make a \acc{D} change, \\ 
just sit \acc{C} down, take it \acc{Am}7 slowly, \\ 
you’re still \acc{G} young, that’s your \acc{Em} fault, \\ 
there’s so \acc{Am} much you have to go \acc{D} through. \\ 
Find a \acc{G} girl, settle \acc{D} down, \\ 
if you \acc{C} want you can \acc{Am}7 marry, \\ 
look at \acc{G} me I am \acc{Em} old but I’m \acc{Am} happy. \acc{D} \\ 
All the \acc{G} times that I’ve \acc{D} cried, \\ 
keeping \acc{C} all the things I \acc{Am}7 knew inside, \\ 
it’s \acc{G} hard but it’s \acc{Em} harder to ig-\acc{Am}-nore it. \acc{D} \\ 
If they were \acc{G} right I’d \acc{D} agree, \\ 
but it’s \acc{C} them they know not \acc{Am}7 me. \\ 
Now there’s a \acc{G} way and I \acc{Em} know that I \acc{D} have \\ 
to \acc{G} go away, \\ 
I \acc{D} know, I \acc{C} have to \acc{G} go.

%\end{enumerate}