% !TeX root = Liederbuchtest.tex
\begin{finalbox}{\artist}
\titlee{Hey Jude}
\end{finalbox}

\begin{enumerate}
\myverse{ Hey \acc{G} Jude, don’t make it \acc{D} bad, \\ 
take a \acc{D7} sad song and make it \acc{G} better. \\ 
Re\acc{C} member to let her into your \acc{G} heart, \\ 
then you can \acc{D} start to make it bet\acc{G} ter. }

\myverse{ Hey \acc{G} Jude, don’t be a\acc{D}fraid, \\ 
you were \acc{D7} made to go out and get \acc{G} her. \\ 
The \acc{C} minute you let her under your \acc{G} skin, \\ 
then you’ll be\acc{D}gin to make it bet\acc{G}ter. \\ 
\acc{G7} And any time you feel the \acc{C} pain, \\ 
Hey \acc{Em} Jude, re\acc{Am}frain, \\ 
don’t \acc{Am7} carry the \acc{D7} world \\ 
upon your \acc{G} shoulders. \acc{G7} \\ 
For now you know that it’s a \acc{C} fool \\ 
who \acc{Em} plays it \acc{Am} cool \\ 
by \acc{Am7} making his \acc{D7} world a little \acc{G} colder. \\ 
Da-da-da \acc{G7} da-da \acc{D7} da-da-da da. }

\myverse{ Hey \acc{G} Jude, don’t let me \acc{D} down, \\ 
you have \acc{D7} found her, now go and \acc{G} get her. \\ 
Re\acc{C} member to let her into your \acc{G} heart, \\ 
then you can \acc{D} start to make it \acc{G} better. \\ 
\acc{G7} So let it out and let it \acc{C} in \\ 
Hey \acc{Em} Jude, be\acc{Am}gin, \\ 
you’re \acc{Am7} waiting for some-
\acc{D7}-one to per\acc{G}form with. \acc{G7} \\ 
And don’t you know that it’s just \acc{C} you, \\ 
Hey \acc{Em} Jude, you \acc{Am} do, \\ 
the \acc{Am7} movement you \acc{D7} need \\ 
is on your \acc{G} shoulder. \\ 
Da-da-da \acc{G7} da-da \acc{D7} da-da-da da }

\myverse{ Hey \acc{G} Jude, don’t make it \acc{D} bad, \\ 
take a \acc{D7} sad song and make it \acc{G} better. \\ 
Re\acc{C} member to let her under your \acc{G} skin, \\ 
then you’ll be\acc{D}gin to make it \acc{G} better. \\ 
better, better, better, better, better, oh! \\ 
|: \acc{G} Da da-da Fda-da-da da, \\ 
\acc{C} da-da-da da, hey \acc{G} Jude. :| }

\end{enumerate}