\title{Lady in Black} 

She \acc{Em} came to me one morning, \\ 
one lonely Sunday morning, \\ 
her \acc{D} long hair flowing in the \\ 
\acc{Em} mid-winter wind. \\ 
I \acc{Em} know not how she found me, \\ 
for in darkness I was walking, \\ 
and \acc{D} destruction lay around me \\ 
from a \acc{Em} fight I could not win. \\ 
\acc{Em} Ahahaaa \acc{D} aahah, \acc{Em} ahahaaa \acc{D} aha \acc{Em} a! \\ 

She \acc{Em} asked me name my foe then. \\ 
I said the need within some men \\ 
to \acc{D} fight and kill their brothers \\ 
without \acc{Em} thought of men or god. \\ 
And I \acc{Em} begged her give me horses \\ 
to trample down my enemies, \\ 
so \acc{D} eager was my passion \\ 
to \acc{Em} devour this waste of life. \\ 
\acc{Em} Ahahaaa \acc{D} aahah, \acc{Em} ahahaaa \acc{D} aha \acc{Em} ah! \\ 

But \acc{Em} she would not think of battle \\ 
that reduces men to animals, \\ 
so \acc{D} easy to begin and yet \acc{Em} impossible to end. \\ 
For \acc{Em} she the mother of all men \\ 
had counciled me so wisely that \\ 
I \acc{D} feared to walk alone again \\ 
and \acc{Em} asked if she would stay. \\ 
\acc{Em} Ahahaaa \acc{D} aahah, \acc{Em} ahahaaa \acc{D} aha \acc{Em} ah! \\ 

»Oh \acc{Em} lady lend your hand,« I cried, \\ 
»Oh let me rest here at your side.«
»Have \acc{D} faith and trust in me,« she said \\ 
and \acc{Em} filled my heart with life. \\ 
There is no strength in numbers. \\ 
I’ve no such misconceptions. \\ 
But \acc{D} when you need me be assured \\ 
I \acc{Em} won’t be far away. \\ 
\acc{Em} Ahahaaa \acc{D} aahah, \acc{Em} ahahaaa \acc{D} aha \acc{Em} ah! \\
